Distribution-oblivious Programming with Dish

### 2019-11-22 pldi/draft.tex
Update acmart
Cleanup

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  \nv{placeholder}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed framework interfaces, or distribution annotations.
% 
%   \emph{Distribution-oblivious programming} is a new approach for..?
  This paper presents \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. %  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known distributability classes.
  \sys's insight is that shell pipelines already express stream computations that can automatically distributed.
  To achieve this, \sys
% a series of techniques for automatically 
decomposes primitives into distributability classes,
identifies high-distributability stages,
applies rewriting rules for largest possible subprograms,
and orchestrates the distributed program.
Its runtime component provides orchestration and planning support during the execution of the program.
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
% 
Experiments for complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}

@@

@@

\subsection{The Shell Language}
\label{bg:shell}

\heading{Implicits}
Expansion
Implicits
Context

\heading{Language Constructs}

Even without these, the Unix pipeline language is powerful enough to capture complex pipelines.

We can encode powerful

>>>>

\acmSubmissionID{248}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed frameworks, or source-level annotations.
  This paper presents \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
  \sys's insight is that shell pipelines already express stream computations that can be automatically distributed.
  To achieve this, \sys
decomposes primitives into distributability classes,
identifies high-distributability stages,
applies rewriting rules for largest possible subprograms,
and orchestrates the distributed program.
Its runtime component provides orchestration and planning support during the execution of the program.
Experiments for complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}

% These are from the abstract:
%  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known distributability classes.
% a series of techniques for automatically 
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
%

@@

% Additional material, in anonymized form, is available at~\href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.

@@
